Estimating duration in the presence of misclassification

### 2024-01-16 cis-imperfect-testing.tex
include false negative estimates

I modified the simulation study from \cref{E-perf-test:sec:simulation-study} to include the possibility of false negatives.
More single positive episodes are seen at lower values of $\psens$ (see \cref{imperf-test:fig:sim-single-pos}).
A value between 60\% and 80\% for $\psens$ reproduces the number of single positive episodes observed within the CIS data.
In \cref{E-ATACCC}, I estimated that the rate of false negatives is\todo{add what the ATACCC false negative rate is}.
The daily testing in the ATACCC study, used for the \cref{E-ATACCC} estimates, should provide a reliable estimate of the false negative rate during the period for which the individuals are followed-up\todo{rephrase this sentence, currently unclear}.
The requirement for a much lower value of $\psens$ suggests this model of false negatives is inadequate.

>>>>

I modified the simulation study from \cref{E-perf-test:sec:simulation-study} to include the possibility of false negatives.
More single positive episodes are seen at lower values of $\psens$, with a value between 60\% and 80\% reproducing the number of single positive episodes observed in the CIS data (see \cref{imperf-test:fig:sim-single-pos}).
In \cref{E-ATACCC}, I estimated that $\psens$ ($1-\rho$ in \cref{E-ATACCC}'s parameterisation) is 95\% (95\% CrI: 96\%--93\%).
The daily testing in the ATACCC study, used for the \cref{E-ATACCC} estimates, means this is a reliable estimate during the period for which the individuals are followed-up.
The requirement for a much lower value of $\psens$ in the simulation study suggests this model of false negatives is inadequate.
